---
title: <center> <h3> Shopify </h3> <h2> Winter Internship 2022 </h2> <h3> done by </h3> <h3> <span style="color:red">*Tugay Balatlı* </span> </h3> </center>
pagetitle: Shopify
params:
 resume_on_error: no
output: 
  bookdown::html_document2:
    theme: readable
    toc: false
---
  
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("ggplot2")
library("readxl")
library("GGally")
library("magrittr")
library("pander")
```

# Explanatory Data Analysis
```{r, fig.asp=1}
data <- data.frame(readxl::read_xlsx("2019 Winter Data Science Intern Challenge Data Set.xlsx"))

summary(is.na(data)) %>% pander()
summary(data) %>% pander()

ggplot(data, aes( x = order_amount)) + geom_density()
ggplot(data, aes( x = order_amount)) + geom_boxplot()
```


$$
\text{Average Order Value} = \text{Revenue} / \text{Number of Orders}
$$

# Outlier Elimination

Here, I eliminated orders that have extremely high order costs which is 704000 and the orders are taken from `shop_id` 78 since its products are way expensive that is 25725 than usual shoe prices.

```{r}
to_del = which(data$order_amount == 704000 | data$shop_id == 78)

new_data <- data[-to_del,]

summary(new_data) %>% pander()

ggplot(new_data, aes( x = order_amount)) + geom_density()
ggplot(new_data, aes( x = order_amount)) + geom_boxplot()
```


The new Average Order Value is 302.6 according to my analysis

# Questions

## Think about what could be going wrong with our calculation. Think about a better way to evaluate this data. 
By checking the dataset, I observed some outliers. This might be a problem while we are trying to calculate a mean value. There are no missing values which is good. As it can be a problem in the modelling phase and generalizable results, we should consider removing the outlier values by checking the quantile values. We can choose a threshold as .75 quantile.

## What metric would you report for this dataset?
If we directly use average value, we might make mistakes. As I indicated in the first question, the mean value can be misleading. Instead, we can report 
several quantile (or percentile) values, such as .5, .25, .50, .75, .95.


## What is its value?
Without outlier elimination,
```{r}
quantile(data$order_amount, c(.05, .25, .5, .75, .95)) %>% pander()
```

With outlier elimination,
```{r}
quantile(new_data$order_amount, c(.05, .25, .5, .75, .95)) %>% pander()
```



